Drivers of sex differences in consumption (NAMCS)

### 2017-06-26 sex-difference/namcs.Rmd
methods

>>>>

## Data & overall methods

I used the 2014 NAMCS data. Because this is a survey, you can't just look at the individual records; they all need to be weighted, and the variances need to be adjusted by the stratum sampling used. I rely on the `survey` package, to which the entry point is the `svydesign` function, for which I use:

- NAMCS's `CPSUM` variable for `ids`
- `CSTRATM` for `strata`
- `PATWT` for `weights`
